Verifying Demonstrations

### 2018-02-26 paper/intro.tex
coincoin

Elaborating on the scenario sketched in the abstract, Alice is an
activist who organizes a protest for some cause.
Eve is an autocrat who opposes Alice's cause.
Bob, Carol and many others participate in the protest for Alice's
cause and thus against Eve. To verify how many participated in Alice's
protest, a reliable crowd-counting mechanism is needed which is a 
problem that has not yet been entirely solved.

@@

Some of our assumptions (see Section \ref{assumptions} for more
detailed descriptions) are not yet
realized. Not all (or even many) protesters, especially in countries
with oppressive regimes, currently possess smartphones. Digital
certificates signed by a central authority are not yet widely
available and if we rely on government-issued credentials, we cannot prevent the government 
from performing Sybil attacks --- since it can issue arbitrarily many 
\enquote{valid} credentials. In this case we cannot verify any pro-government protests where Eve's authoritarian regime wants to organize a pro-regime protest to 
demonstrate its \enquote{wide 
  support}~\cite[e.g.][]{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
Distance bounding on phones is currently not feasible within a
meaningful range of distance for our scenario.

>>>>

Consider the following scenario in which Alice is an activist that organizes a protest against the current regime leader Eve in some location(s).
On one hand, Alice wants to estimate the number of participants to prove a certain support for her cause.
On the other hand, Eve is an autocrat who opposes Alice's cause.
Bob, Carol and many others participate in the protest for Alice's cause against Eve.
However, they might also be willing to do so in a manner that does not leave any digital traces because of the fear of retribution against them from Eve's regime. 
To verify how many participated in Alice's protest, a reliable yet privacy-preserving crowd-counting mechanism is needed, which to the best of our knowledge is a problem that has not yet been entirely solved.

@@

Some of our assumptions (see Section \ref{assumptions} for more
detailed descriptions) are not yet
realized. Not all (or even many) protesters, especially in countries
with oppressive regimes, currently possess smartphones. Digital
certificates signed by a central authority are not yet widely
available and if we rely on government-issued credentials, we cannot prevent the government 
from performing Sybil attacks --- since it can issue arbitrarily many 
\emph{valid} credentials. In this case we cannot verify any pro-government protests where Eve's authoritarian regime wants to organize a pro-regime protest to 
demonstrate its \emph{wide 
  support}~\cite[e.g.][]{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
Distance bounding on phones is currently not feasible within a
meaningful range of distance for our scenario.
